
MINUTES 2

Speedup number where did it come from?

How do you test the speedup? rn Mbps

Plan for locking mechanism? read locks write locks? Integrity of data. Permissions producer consumer problem. Consistency of data? Sabay put and get who gets it first?

By next year magpoprovide ng PCs. Physical PC will be from PGC.

UI? Di problem yung UI.
one for upload.
one for download.
one for file list, uTorrent.

FOCUS IN TRANSFER

Pros cons ng distributed ng peer to peer
How they apply to needs of problem
Maraming online di lang NCBI it is a common framework na.

Not clear. Why not have it on a smaller scale? Abstract pros and cons for diff approaches. May proposed schematic. Di diniscuss bakit yun and how it addresses needs. Di justified why ito yung architecture.

Ano yung problem? And why this specific problem is being solved by this theore framework

Di clear. We went straight to special databases and not normal databases. Why not current databases lang. Why couldnt pgc not just have an ftp server.

May plan but it isnt clear why there is a plan? What exactly are you trying ifix? What has been tried to fix before.

Does the user select between data node and master node? Can choose a mirror esque

Cant see the important aspect. Data model of database. What data is being distributed? What you capture information? What you store?

Copy it from Seqtorr -> Also Cite it

How would you store them? How you distribute? May preprocessing of data ba? Types of files? How you store?

A more specific layer. File name. Header. Sequence. Date uploaded? Species? Length of sequence?

Do we have multiple tables? Use muna data model of seqtorr? Master node that contains the metadata? If it only has metadata? Does it mirror to other data nodes?

Multiple metadata nodes? Can data nodes do what master nodes does? What if master node fails? Can you mirror the metadata to other data nodes? Master node distributes the data and kahit magfail yung main node. Suggest: remove master node keep metadata for all.

Why master node?